Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-01-15 Latex/journal_v1/Resource Allocation in an Open RAN System using Network Slicing-.1cm (1)/pr.tex
first commit for new git

In this section, we describe the downlink system in O-RAN with slicing as depicted in Figure \ref{fig:c11}. 
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
There are three service types including mMTC, eMBB, and uRLLC, which support different applications. There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and uRLLC service types, respectively and we have $S = S_1 + S_2 + S_3$. {\color{red} explain pre-allocated more}
Therefore, there are $S$ pre-allocated slices serving these $S$ services;
Each pre-allocated slice contains reserved VNFs for the MAC/RLC functions in the O-DU logical node, the PDCP/SDAP functions in the O-CU-UP, and the UPF nodes. 
 There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (uRLLC), and $S_3$ slices for the third service type (mMTC). So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.

Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of 
%pre-allocated virtual resource blocks that are mapped to the Physical Resource Blocks (PRBs),
 $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.

All $K$ PRBs can be assigned to all UE in each service.
Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.

@@

\noindent where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association. Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association. Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is the matrix that shows the number of VNFs in each layer of slice.

@@

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the uRLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{equation}
\begin{split}
\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}\\
\end{split}
\end{equation}
Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability. We notice that it makes the formulation simpler. However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner. Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and 
\begin{equation}
\begin{split}
T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
\end{split}
\end{equation}
\begin{lemma}

{\color{red} add one sentence before lemma to motivate why you need this lemma. The whole part is a lemma? It is too long. Where is the proof?}

In problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as
$ \forall i,\forall s$
\begin{equation}
\begin{split}
&T^{\max}_s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
&M_s \geq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\
\end{split}
\end{equation}
Also from equations in \eqref{c19}, \eqref{c16-1} and \eqref{c16-3}, we have
\begin{equation}
\alpha_s/\mu_s\leq M_s \leq \min\{M^{\max}, \phi_{\max}/{3\phi_s}\}
\end{equation}
We denote $ \mathfrak{M}_s= \min\{M^{max}, \phi_{max}/{3\phi_s}\}$.
Thus, if we restrict constraint \eqref{c16} to equality, constraint \eqref{c16} is still valid.
Also, we have the following inequality.
\begin{equation}\label{eqDelay}
\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
\end{equation}
In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 
the numerator and the denominator will both have the same sign.
In the numerator, according to the \eqref{c16-2}, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$, and as we know that $\alpha_s \geq 0$, we have $ \alpha_s (R_{u(s,i)}-\lambda_{u(s,i)}) \geq 0 $.
If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$, the numerator will be positive.
$(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$ since the order of $T^{max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{max}_s$.
Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{max}_s$.
So the numerator will be positive.
In the denominator, we can say that $(T^{max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,  
$\mu_s \geq 0$ and
$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{max}_s$ as mentioned above.
%Therefore, we need to have the constraint below.
%\begin{equation}\label{constraint16}
%\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
%\end{equation}

@@

In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
So to obtain, the optimal number of activated VNF in each slice, we need to find the maximum of the
$\mathtt{M}_{u(s,i)}$ in each slice as follow.
\begin{equation}
M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
\end{equation}
\end{lemma}
Despite simplifying the problem in \eqref{problem}, it is still non-convex and hard to solve.
Therefore, the conventional approach to solve the problem of the PRB and the power allocation is to relax the variable $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$ \cite{lee2018dynamic,ali2018joint}.
Furthermore, the problem can be solved using the Lagrangian function and iterative algorithm.

@@

Assume, UE $i$ in the slice $s$ that is associated to the O-RU $r$, is allocated to the PRB $k$  ($e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition. 
\begin{equation}\label{deriveP}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
 &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0\\
\end{split}
\end{equation}
where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follow.
\begin{equation}
\begin{split}
\mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
\end{split}
\end{equation}
Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
The optimal power is as follow.
\begin{equation}
\begin{split}
p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
\end{split}
\end{equation}
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
\begin{equation}\label{deriveE}
\begin{split}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
\end{split}
\end{equation}
So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
\begin{equation}\label{deriveE1}
\begin{split}
e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
\end{split}
\end{equation}
where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
\begin{equation}
e_{r,u(s,i)}^{k} = 
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S\\
      0 & \text{otherwise}
    \end{cases}
\end{equation}
Where, $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
 \end{lemma}
Thus the user in each slice $s$ that have the the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to the PRB $k$. Since just one PRB can be allocated to a UE between those UEs (regardless to the services) that are associated to the same O-RU.
The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
The complexity order of this problem is about $O( T_{conv} \times\mathfrak{N} \times K)$.
\subsection{Sub-Problem 2}\label{sub2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.

@@

In this section, firstly we describe the initial points and the comparison algorithms.
Then we talk about the feasible region in our system. 
Afterward, we illustrated the numerical results.
\subsection{The initial Points and The Comparison Algorithms}
In this part, numerical results for the main problem are depicted to evaluate the performance of the algorithms using the Monte-Carlo method. We consider three network slices for eMBB, uRLLC, and mMTC services.
Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in figure \ref{fig:cell}. In addition, we consider the users placed randomly in this place.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.47]{cell.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{O-RU placement in a cell}
  \label{fig:cell}
\end{figure}
Here, the channel vector from the O-RU $r$ to the UE $i$ in service $s$ is set as $\bold{h}_{r,u(s,i)}^{k}=d_{r,u(s,i)}^{-\mathcal{L}} \Omega_{r,u(s,i)}^{k} $.  Where, $d_{r,u(s,i)}^{-\mathcal{L}} $ is the distance between the O-RU $r$ and the UE $i$ in service $s$ and $\mathcal{L} = 3.8$ is the path-loss exponent \cite{gholipoor2020cloud}.
Also, $\Omega_{r,u(s,i)}^{k}$ is the random variable that is generated by the Rayleigh distribution
and it is the Rayleigh fading channel between the UE and O-RU.
We consider 25 PRBs are used in the network and the
packet size is equal to 20 bytes.
The maximum number of VNF for each slice is 25 and the mean arrival data rate for the eMBB service is $\lambda  = 3Mbps$ and for the mMTC service and the uRLLC  service is $\lambda  = 0.2Mbps$. 
Also the quantization noise is assumed to be $10^{-13}$.
Moreover, we set $\mathfrak{h}_{u_{(s,i)}} = \eta_{u_{(s,i)}}/200$, $\mathfrak{m}_{r} = \zeta_r/10$
and $\mathfrak{q}^k_{r,u(s,i)} = P_{s}^{max}/100$.

>>>>

In this section, we describe the downlink system in O-RAN with slicing as depicted in Figure \ref{fig:c11}. 
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
There are three service types including mMTC, eMBB, and URLLC, which support different applications. There are $S_1$, $S_2$ and $S_3$ different applications for the mMTC, eMBB and URLLC service types, respectively and we have $S = S_1 + S_2 + S_3$. 
%{\color{red} explain pre-allocated more}
Therefore, there are $S$ pre-allocated slices serving these $S$ services;
Each pre-allocated slice contains reserved VNFs for the three logical nodes:
\begin{itemize}
\item The MAC/RLC functions in the O-DU logical node
\item The PDCP/SDAP functions in the O-CU-UP logical node
\item The UPF logical node
\end{itemize}

 There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC). So, each service request $s\in \{1,\ldots,S\}$ is served by its corresponding slice.

Each Service $s_j\in \{1,2,...,S_j\} $ consists of $U_{s_j}$ requests from  single-antenna UEs which require certain level of QoS. We notice that $j \in \{1,2,3\}$ indicates the service type.
There are different application requests which fall into one of these service categories. Each application request requires a specific QoS. Based on the application and QoS request, UE may be admitted and allocated to the resources.
Each slice $s_j \in \{1,2,...,S_j \}$, $j \in \{1,2,3\}$ consists of  $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF are required.

Assume we have $K$ physical resource blocks (PRBs) in this system.
All $K$ PRBs can be assigned to all UEs in each service.
Also, each VNF instance runs on a virtual machine (VM) that uses resources from the data centers.

@@

\noindent where $\bar{\mathcal{R}}_{u_{(s,i)}}, \:\:\forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
In addition, $\boldsymbol{P} =[p_{r,u(s,i)}^{k}], \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k], \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association. Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r], \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association. Furthermore, $M = [M_s^d, M_s^c, M_s^u], \:\: \forall s$ is the matrix that shows the number of VNFs in each layer of slice.

@@

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{s}^{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}, to convexify the \eqref{eq11} for the URLLC and mMTC services that have the short packet transmission.
So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{equation}
\begin{split}
\bar{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \bar{\rho}_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\bar{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\bar{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}\\
\end{split}
\end{equation}
Without loss of generality, assume that UPF, O-CU and O-DU use the processors with the same processing capability. We notice that it makes the formulation simpler. However, loosing this assumption does not change the formulation significantly and the problem can be solved in the same manner. Therefore, we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). So $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. Again, this assumption only simplifies the notations and loosing it does not make the solution inefficient.
These assumptions lead to having the same processing power for each layer $\phi_s^u = \phi_s^c =\phi_s^d $.
As a result, we have $M_s = M_s^u = M_s^c = M_s^d $.
Using the above assumption, we have $T^{DU}_{s} = T^{CU}_{s} = T^{UPF}_{s}$ and 
\begin{equation}
\begin{split}
T^{\text{proc}}_{s} &=  T^{RU}_{s} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s} \\
                     &=  T^{RU}_{s} + 3\times T^{DU}_{s}.
\end{split}
\end{equation}
In the following, we define a lemma to find the upper and lower bound for the optimal number of VNFs based on the achievable rates. Afterward, we obtain the formula to attain the optimal number of VNFs.  
\begin{lemma}
The optimal number of VNFs in each slice s can be achieved by the 
$M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s$.
where, $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.

\end{lemma}
%{\color{red} add one sentence before lemma to motivate why you need this lemma. The whole part is a lemma? It is too long. Where is the proof?}
\begin{proof}
In problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as
$ \forall i,\forall s$
\begin{equation}
\begin{split}
&T^{\max}_s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
&M_s \geq \frac{\alpha_s(T^{\max}_s R_{u(s,i)}-T^{\max}_s\lambda_{u(s,i)} -1)}{(T^{\max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\
\end{split}
\end{equation}
Also from equations in \eqref{c19}, \eqref{c16-1} and \eqref{c16-3}, we have
\begin{equation}
\alpha_s/\mu_s\leq M_s \leq \min\{M^{\max}, \phi_{\max}/{3\phi_s}\}
\end{equation}
We denote $ \mathfrak{M}_s= \min\{M^{max}, \phi_{max}/{3\phi_s}\}$.
Thus, if we restrict constraint \eqref{c16} to equality, constraint \eqref{c16} is still valid.
Also, we have the following inequality.
\begin{equation}\label{eqDelay}
\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
\end{equation}
In equation \eqref{eqDelay}, $0\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 
the numerator and the denominator will both have the same sign.
In the numerator, according to the \eqref{c16-2}, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$, and as we know that $\alpha_s \geq 0$, we have $ \alpha_s (R_{u(s,i)}-\lambda_{u(s,i)}) \geq 0 $.
If we assume that the $(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$, the numerator will be positive.
$(R_{u(s,i)}-\lambda_{u(s,i)})T^{max}_s \geq 1$ since the order of $T^{max}_s$ is about milli second and the difference between achievable rate and packet rate can be more than $1/T^{max}_s$.
Therefore, to ensure that this constraint will be valid, we restrict constraint \eqref{c16-2} to $R_{u(s,i)} \geq \lambda_{u(s,i)} + 1/T^{max}_s$.
So the numerator will be positive.
In the denominator, we can say that $(T^{max}_s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \geq 0 $, since,  
$\mu_s \geq 0$ and
$(R_{u(s,i)}-\lambda_{u(s,i)}) \geq 1/T^{max}_s$ as mentioned above.
%Therefore, we need to have the constraint below.
%\begin{equation}\label{constraint16}
%\alpha_s/\mu_s\leq \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
%\end{equation}

@@

In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T^{max}_s R_{u(s,i)}-T^{max}_s\lambda_{u(s,i)} -1)}{(T^{max}_s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ for each UE $i$ in slice $s$.
So to obtain, the optimal number of activated VNF in each slice, we need to find the maximum of the
$\mathtt{M}_{u(s,i)}$ in each slice as follow.
\begin{equation}
M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
\end{equation}
\end{proof}

Despite simplifying the problem in \eqref{problem}, it is still non-convex and hard to solve.
Therefore, the conventional approach to solve the problem of the PRB and the power allocation is to relax the variable $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$ \cite{lee2018dynamic,ali2018joint}.
Furthermore, the problem can be solved using the Lagrangian function and iterative algorithm.

@@

\end{lemma}
\begin{proof}
Assume UE $i$ in slice $s$, associated with O-RU $r$, is allocated to PRB $k$  (i.e., $e_{r,u(s,i)}^{k} = 1$). Therefore, we have the following KKT condition
\begin{equation}\label{deriveP}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
 &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0,\\
where $ \mathfrak{s}^k_{r,u(s,i)}=\kappa^k_{r,u(s,i)}-\mathfrak{q}^k_{r,u(s,i)}$ and other parameters are as follows:
\mathfrak{D}_{r,u(s,i)}^{k} &= \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e^k_{r,u(s,i)}, \\
\mathfrak{B}_{r,u(s,i)}^{k} &= \frac{B |{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 g_{u(s,i)}^r e_{r,u(s,i)}^{k}}{\ln(2)} \mathfrak{S}_{r,u(s,i)}^{k},\\
\mathfrak{S}_{r,u(s,i)}^{k} &= \frac{1}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2 \mathfrak{k}_{r,u(s,i)}^{k}+BN_0 + I_{r,u(s,i)}^{k}}.\\
Also, $\mathfrak{k}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}p_{r,u(s,i)}^{k}$.
Thus, from equation \eqref{deriveP}, optimal power is obtained and power is allocated.
We denote $ \mathfrak{j}_{r,u(s,i)}^{k} = g_{u(s,i)}^r e_{r,u(s,i)}^{k}$.
The optimal power is as follow.
p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ Ln2 \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.\\
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
\begin{equation}\label{deriveE}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.\\
So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
\begin{equation}\label{deriveE1}
e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
e_{r,u(s,i)}^{k} = 
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S, \\
      0 & \text{otherwise,}
    \end{cases}
where $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
 \end{proof}
Thus, the user in slice $s$ that has  the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to PRB $k$. Since just one PRB can be allocated to a UE between those UEs (regardless of the services), that is associated to the same O-RU.
The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
The complexity order of this problem is about $O( T_{conv} \times\mathfrak{N} \times K)$.
\subsection{Sub-Problem 2}\label{sub2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.

@@

In this section, firstly, we describe the initial points and the comparison algorithms.
Then, we talk about the feasible region of our system model. Afterward, we illustrate the numerical results.
